Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-04-14 paper/abstraction/paper.tex
tinker acks

\para{Acknowledgments}
We thank the many network engineers, especially George Chen and Lihua Yuan, who helped us understand the importance of working with abstract topologies and synthesizing templates. 
We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.

>>>>

\para{Acknowledgments}
We thank the many network engineers, especially George Chen and Lihua Yuan, who pointed out the importance of working with abstract topologies. 
We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 as well as Cisco award 677002.
